PID Controller Implementation in CARLA Simulator

### 2024-12-02 Article.tex
Article.tex

This project successfully demonstrated the implementation of a PID controller in the CARLA simulator for autonomous vehicle control. By fine-tuning the PID parameters, the vehicle accurately followed predefined routes and maintained the target speed, validating the defined hypotheses. The lateral error analysis showed effective path tracking, especially in straight-line segments, while performance during sharp 90-degree turns indicated areas for improvement.

Although CARLA offers advanced route planning capabilities using automatic pathfinding, this work intentionally utilized more rudimentary methods. This approach allowed for a deeper understanding of the simulator and explored how CARLA's camera features can be leveraged in future research.

Future work could involve exploring more advanced control strategies or adaptive PID tuning to enhance performance in complex driving scenarios. Additionally, varying the vehicle's speed, adding turns that are not 90 degrees, experimenting with different simulation environments, and integrating computer vision techniques could lead to a fully autonomous vehicle without the need for manual route planning.

>>>>

This project successfully demonstrated the implementation of a PID controller for autonomous vehicle control within the CARLA simulator. By fine-tuning the PID parameters, the vehicle accurately followed predefined routes and maintained the target speed, thereby validating the defined hypotheses. The lateral error analysis indicated effective path tracking, particularly in straight-line segments; however, performance during sharp 90-degree turns highlighted areas for potential improvement.

Although CARLA provides advanced route planning capabilities with automatic pathfinding, this project intentionally employed more rudimentary methods. This approach facilitated a deeper understanding of the simulator and enabled exploration of how CARLA's camera features can be leveraged in future research.

Future work may involve investigating advanced control strategies or adaptive PID tuning to improve performance in complex driving scenarios. Moreover, varying the vehicle's speed, incorporating turns of various angles, experimenting with different simulation environments, and integrating computer vision techniques could facilitate the development of a fully autonomous vehicle without the need for manual route planning.
